Longitudinal Principal Manifold Estimation

### 2024-04-05 paper/main.tex
fix figure reference

Considering the same individual shown in Figures \ref{fig:adni_result} and \ref{fig:adni_cross_section}, results of fitting the PME and LPME algorithms to the surface of the left thalamus are shown in Figures \ref{fig:adni_lthal_result} and \ref{fig:lthal_cross_sections}. While the segmentation estimates of the thalamus do not show the same sort of deviations that are clearly visible for the hippocampus, the cross section plots shown in Figure \ref{fig:lthal_cross_sections} indicate that both the PME and LPME algorithms show a closer fit to the more regularly shaped thalamus surface than was achieved for the hippocampus.

>>>>

Considering the same individual shown in Figures \ref{fig:adni_result} and \ref{fig:lhipp_cross_sections}, results of fitting the PME and LPME algorithms to the surface of the left thalamus are shown in Figures \ref{fig:adni_lthal_result} and \ref{fig:lthal_cross_sections}. While the segmentation estimates of the thalamus do not show the same sort of deviations that are clearly visible for the hippocampus, the cross section plots shown in Figure \ref{fig:lthal_cross_sections} indicate that both the PME and LPME algorithms show a closer fit to the more regularly shaped thalamus surface than was achieved for the hippocampus.
